### 2016-01-21 paper.tex
Add pertinent results to abstract and conclusion; resolves #33

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. Weak linear $Re$-dependence was achieved
at a turbine diameter Reynolds number $Re_D \approx 10^6$. The effects of blade
support strut drag on turbine performance were investigated by covering the
rotor's NACA 0021 struts with cylinders. As expected, this modification
drastically reduced the rotor power coefficient. Strut drag was also measured
for the NACA 0021 and cylindrical configurations with the blades removed. An
optimal tip speed ratio $\lambda_0 = 3.1$ was chosen, at which the near wake
velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity, turbulence
kinetic energy, and mean kinetic energy transport were compared with results
from a high solidity turbine acquired with the same test apparatus. Overall,
lower levels of streamwise wake recovery were calculated for the RM2 case---a
consequence of both the relatively low solidity and tapered blades reducing
blade tip vortex shedding---responsible for mean vertical advection---and lower
levels of turbulence caused by higher operating tip speed ratio and therefore
reduced dynamic stall.

@@

The performance and near-wake velocity of a 1:6 scale DOE Reference Model 2
cross-flow turbine was measured in a towing tank.

@@

While operating at its optimal tip speed ratio $\lambda=3.1$ the wake at
$x/D=0.93$ downstream was shown to be relatively symmetrical and lacked the
evidence of strong blade stall, both of which differentiate this near-wake from
the higher solidity, lower $\lambda_0$ UNH-RVAT. Terms from the mean kinetic
energy transport equation were also computed in this $y$--$z$ plane, showing the
relative importance of the vertical advection compared with turbulent transport
terms at this location. It is interesting to note that though the RM2 is a more
effective energy converter than the UNH-RVAT, its wake recovery may in fact be
delayed due to weaker blade tip vortex shedding and lower levels of turbulence
in the near-wake.

>>>>

The mechanical power, total rotor drag, and near-wake velocity of a 1:6 scale
physical reference model vertical-axis cross-flow turbine were measured
experimentally in a towing tank, to provide a comprehensive open dataset for
validating numerical models. Performance was measured at multiple Reynolds
numbers by varying tow carriage speed. A peak power coefficient $C_P = 0.37$ and
rotor drag coefficient $C_D = 0.84$ were observed at an optimal tip speed ratio
$\lambda_0 = 3.1$. Weak linear $Re$-dependence was achieved at a turbine
diameter Reynolds number $Re_D \approx 10^6$. The effects of blade support strut
drag on turbine performance were investigated by covering the rotor's NACA 0021
struts with cylinders. As expected, this modification drastically reduced the
rotor power coefficient. Strut drag was also measured for the NACA 0021 and
cylindrical configurations with the blades removed. For $\lambda=\lambda_0$,
wake velocity was measured at 1 m $(x/D=0.93)$ downstream. Mean velocity,
turbulence kinetic energy, and mean kinetic energy transport were compared with
results from a high solidity turbine acquired with the same test apparatus. Like
the high solidity case, mean vertical advection was calculated to be the largest
contributor to near-wake recovery. However, overall, lower levels of streamwise
wake recovery were calculated for the RM2 case---a consequence of both the
relatively low solidity and tapered blades reducing blade tip vortex
shedding---responsible for mean vertical advection---and lower levels of
turbulence caused by higher operating tip speed ratio and therefore reduced
dynamic stall. However,

@@

The performance and near-wake velocity of a 1:6 scale DOE Reference Model 2
cross-flow turbine was measured in a towing tank. A maximum power coefficient
$C_P = 0.37$ and rotor drag coefficient $C_D = 0.84$ were observed at an optimal
tip speed ratio $\lambda_0 = 3.1$.

@@

While operating at its optimal tip speed ratio $\lambda=3.1$ the wake at
$x/D=0.93$ downstream was shown to be relatively symmetrical and lacked the
evidence of strong blade stall, both of which differentiate this near-wake from
the higher solidity, lower $\lambda_0$ UNH-RVAT. Terms from the mean kinetic
energy transport equation were also computed in this $y$--$z$ plane, showing the
relative importance of the vertical advection compared with turbulent transport
terms at this location, which is qualitatively similar to the UNH-RVAT wake
data. However, lower wake recover totals were calculated. This indicates that
although the RM2 is a more effective energy converter than the UNH-RVAT, its
wake recovery may in fact be delayed due to weaker blade tip vortex shedding and
lower levels of turbulence in the near-wake, which may present a trade-off when
considering optimal array layouts.
